Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-08 paper/ms.tex
clean up latex; stage table CSV files and readme

\author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
\affiliation{\princeton}
%
%\author{-----SUGGESTED CONTRIBUTORS, PENDING DISCUSSION, COMMENTS, ANALYSES, ETC-----}
%%
%
%\author[0000-0002-3164-9086]{Maximilian N. G\"unther}
%\affiliation{\esa}
%
%\author[0000-0003-2058-6662]{George~R.~Ricker}
%\affiliation{\mitkavli}

@@

In both models, the corotation radius is the location at which matter
concentrates.  The empirical basis for this is that
the sharp CPV features are superposed over smooth, quasi-sinusoidal
starspot profiles.  The theoretical importance of the corotation
radius has been noted in previous studies of magnetic rotators
\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,1991ApJ...370L..39K,2005ApJ...634.1214L}.
%
%including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
%massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
%Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  
%
In regions where the magnetic field dominates the flow (i.e.~$B^2/8\pi
> \rho v^2 /2$), matter is dragged along with the field lines.  
Within such regions, charged gas or dust can become trapped at corotation because
of the four relevant forces -- gravity, Lorentz, inertial
Coriolis, and inertial centrifugal -- the Lorentz and Coriolis only
act perpendicular to field lines, while gravity and the centrifugal
force are in balance at $R_{\rm c}$ \citep[e.g.][their
Section~2]{2005MNRAS.357..251T}.  Another way to phrase this statement
is that, in the corotating frame, the effective potential experienced
by charged particles tends to have local minima at $R_{\rm c}$; given
a flow from either the star or from a tenuous accretion disk, this
local potential minimum enables material to build up
\citep{2005MNRAS.357..251T}.

@@

We searched for CPVs by analyzing the short-cadence data acquired
by TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
Specifically, we used the 2-minute cadence light curves produced by
the Science Processing and Operations Center at the NASA Ames Research
Center \citep{2016SPIE.9913E..3EJ}.  While the TESS data products from
these sectors also included full frame images with cadences of 10 and
30 minutes for a larger number of sources, we restricted our
attention to the 2-minute data for the sake of uniformity and
simplicity in data handling.  In exchange, we sacrificed both
completeness and homogeneity of the selection function.  While TESS
cumulatively observed $\approx$90\% of the sky for at least one lunar
month between 2018 July and 2022 September, the 2-minute cadence
data were collected for only a subset of observable stars that were
preferentially nearby and bright \citep[see][]{2021PASP..133i5002F}.
The total 2-minute data volume
from Sectors 1-55 included 1{,}087{,}475 short-cadence light curves, which were
available for 428{,}121 unique stars.
% latter stats from MERGED_spoc2min_sector1_to_sector58.csv

@@

Peaks of significance were found for $\approx$10\% of the searched
stars.  For all such cases, we generated an interim ``summary sheet''
with information about the star, its full and folded light curves,
Fourier transform, potential contaminating stars, and information
about these contaminating stars.  We then reviewed each summary sheet,
and tentatively classified each light curve based on visual inspection
of its morphology (with common categories including eclipsing binary,
CPV, RS CVn, and cataclysmic variable).
%Whenever a CPV was identified, the light curves from
%multiple sectors were stitched together and analyzed jointly, for a
%more accurate period determination.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f3.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf Validation plots used to classify CPVs}.  The complete figure
      set, with one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable} is available in the online
      journal. {\bf For internal collaboration review:
      \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
      Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
      {\it c)}: DSS finder chart, with 21$''$ and 42$''$ radius
      circles for scale.  One TESS pixel has a full side length of
      21$''$.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram. The gray
      background denotes stars within 100\,pc from
      \citet{2021A&A...649A...6G}.
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN\,$\Sigma$ v1.2 association probabilities,
      calculated using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f4.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CPVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CPVs in the high quality sample.  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Objects are ordered such
      that sources with the most TESS data available are on top (see
      Section~\ref{sec:catalog}).  Zero phase is chosen to correspond
      to minimum light.  Each panel is labeled by the TIC identifier,
      the TESS sector number, the period in hours, and the three-bit
      binarity flag from Table~\ref{tab:thetable}, which denotes Gaia
      DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
      \texttt{ruwe} outliers (bit 2), and stars with secondary TESS
      periods (bit 3). 
		}
		\label{fig:cqvs}
	\end{center}
\end{figure*}

@@

Figure~\ref{fig:cqvs} is a mosaic of phased light curves for the
\ngoods\ CPVs.  The objects are sorted first in order of the number of
TESS 2-minute cadence sectors in which they clearly demonstrated the
CPV phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 (12 sectors);
TIC~402980664 (7 sectors); TIC~89463560
(5 sectors); TIC~363963079 (5 sectors); and
TIC~294328887 (4 sectors).  The brightest five CPVs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.

@@

% Our three ``possible'' infrared excesses were TIC~405910546,
% 289840926, and 244161191.  After a literature search, we concluded
% that none have clear evidence for the presence of a disk.
% TIC~405910546, in LCC, shows a unique TESS light curve, reminiscent of
% a $P$=38\,hr singly-eclipsing binary, except with additional
% substructure during each eclipse that resembles the CPV phenomenon
% more than any other variability of which we are aware.  TIC~289840926
% ($\beta$~Pic moving group, $P$=4.8\,hr), shows what we believe is a
% clear CPV signal, but has no definitive evidence for a large, dusty
% disk.  TIC~244161191 (TOI-278), in Columba, also has no definitive
% evidence for a large disk.  It is however ``multi-periodic''---in
% addition to the 7.17\,hr CPV signal, this source shows a superposed
% 8.39\,hr sinusoidal signal, probably from an unresolved neighboring
% star or binary companion.

@@

TIC~142173958 and TIC~425937691 both show evidence for two separate CPV
signals in their TESS light curves.  For TIC~142173958, the signals
have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691, the two
periods are 4.82\,hr and 3.22\,hr, near the 3:2 period commensurability.
Given that both sources have two photometric signals and elevated
RUWEs, each source is probably an unresolved binary consisting of two
CPVs.  To our knowledge, these are the third and fourth such systems
known: EPIC~204060981 has two CPVs with periods of 9.59\,hr and
9.12\,hr \citep{2018AJ....155...63S}, and TIC~242407571 has two CPVs
with periods of 11.33\,hr and 13.63\,hr, near the 6:5 period commensurability
\citep{2021AJ....161...60S}.
%\footnote{TIC~242407571, although within
%our nominal distance and brightness limits, was not observed by TESS
%in the 2-minute cadence mode between 2018~July and 2022~September, and
%is therefore not in our sample.}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.6cm}
		\caption{
			{\bf Evolution of CPV light curves over two years.}
			Out of the \ngoods\ CPVs in Figure~\ref{fig:cqvs}, 32 had
			2-minute cadence TESS data available for a baseline of at
			least two years; the 27 brightest are shown here due to space
			constraints.  Each panel shows one sector of TESS data, and is
			phased to its deepest minimum in flux.  Each panel's title shows
			the TIC identifier and period in hours.  Text insets
			show the TESS sector numbers, which generally span two years, or
			at least 1{,}000 cycles.  The vertical scale is fixed across
			sectors to clarify shape changes.  Gray circles are raw 2-minute
			data; colored circles bin to 300 points per cycle. 
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

Based on the
fraction of sources overall that ``turned off'', the observed shape
evolution implies that CPVs have an on-off duty cycle of $\approx$75\%.
Correcting for the duty cycle might be important in population-level
estimates of the intrinsic frequency of the CPV phenomenon
\citep[e.g.][]{2022AJ....163..144G}.

@@

% 16 px vs 310 px for a full phase
% Based on our SED fitting $R_\star=0.369\,R_\odot$ star, and from the
% isochrone mass, $M_\star=0.215\,M_\odot$

@@

Curiosities include the four binary systems that are now known to each host
two separate CQVs.
CQVs are sufficiently rare that such systems may have 
physical import.
Recent work has shown that the orbits of binaries closer than
$\lesssim$700 AU tend to be aligned with their planetary systems
\citep[e.g.][]{2022AJ....163..207C}.  If we assume that observing CPV
variability requires high line-of-sight inclinations,
and that the inclinations in binaries are correlated, then we would
expect the detection of one CPV in a binary system to raise the
probability that the other star is a CPV.  The limitations of the
current catalog prevent further exploration of this issue, but it
might be interesting for future study.

A separate possible relation between binarity and CPVs is that the presence
of a binary companion could cause early disk dispersal,
freeing the star to contract.  The CPV phenomenon seems to require
rapid rotation; thus if binary systems tend to produce more rapidly
rotating stars, we would expect a sample of CPVs to have a larger
binary fraction than the field.  However, we see minimal evidence for
such an effect (Section~\ref{subsec:resultsbinarity}).  The
multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
\citep{2019AJ....157..216W}.  
%Based on the same study, the peak of the
%separation distribution decreases from $\approx$49\,AU for
%$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
%$0.15$-$0.30$\,$M_\odot$ M dwarfs.
The $\approx$32\% multiplicity fraction in our
CPV sample (from RUWE$_{\rm DR3}$; see Section~\ref{subsec:resultsbinarity})
seems approximately
consistent with this field fraction.

@@

Examining Figure~\ref{fig:cqvs}, it is clear that CPV dips can be
asymmetric but it is not obvious whether there is a preference for
sharper ingresses or sharper egresses.  In some cases (e.g.
TIC~425933644), the flux variations do not resemble isolated dips,
making the meaning of ``ingress'' and ``egress'' unclear.  In other
cases, such as Sector~36 of TIC~89463560, there is a sharp drop with
an exponential return to the baseline flux, resembling the signatures
of exocomets \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
and the outflowing exospheres of some transiting planets
\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.

@@

Both the dust clump and the gas prominence scenarios (Figure~\ref{fig:f1} and Section~\ref{sec:intro})
invoke clumps
of material at the corotation radius;
the main property that we believe distinguishes the two ideas is 
the composition of the material.

@@

Assuming for the moment that the obscuring material is dust, we can
estimate the mass of a transiting clump. First, we convert the transit
depth into an effective cloud radius, $R_{\rm cloud}$.  For most CPVs
in Figure~\ref{fig:cqvs}, this yields $\approx$2-20\,$R_\oplus$.  A
minimum constraint on the number density of dust particles is obtained
by requiring the cloud to be optically thick.  For cases like LP
12-502, this is reasonable because the transit duration of the
shortest dips implies $R_{\rm cloud}\ll R_\star$.  Carrying out the
relevant calculation assuming the dust grains are 1\,$\mu$m in size,
\citet{2023MNRAS.518.4734S} reported minimum cloud masses of order
$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
optical depth and dust grain radius.  This is comparable to a small
asteroid; the asteroid belt itself has a mass of order
$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  A similar
calculation that assumed occulting clumps of hydrogen, rather than
dust, derived gas prominence masses of at least $10^{14}$\,kg
\citep{1990MNRAS.247..415C}, about 100$\times$ larger than the lower
limit on the dust mass.

If the disappearance of a dip represents the permanent loss of the
obscuring material -- for example, if it is the result of a dust clump
being accreted or ejected -- then we can also estimate the rate at
which mass is flowing through the structures that lead to dips.  For
instance, LP~12-502 showed three ``state-switch'' events over the six
months of available TESS observations, during cycles 261, 309, and
1241 (Figure~\ref{fig:lpriver0}).  The other source for which we
performed a comparable analysis, TIC~300651846
(Appendix~\ref{app:tic3006}), showed two state-switches over 11
months.  In all such cases, at least one dip turned off.  For purposes
of estimation, we will take LP 12-502 as our prototype.  Assuming the
occulting material is dust, the corresponding $\dot{M} \equiv M\cdot
{\rm d}N/{\rm d}t$ time-averaged over six months is
%$\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1}
$\approx
1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
over the $\approx$$10^8$ years for which the CPV phenomenon is
observed, this yields a cumulative moved dust mass of
$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.  If
the occulting material is gas, the lower mass bounds would be of order
100 times larger.  For cases in which we observe the {\it growth} of
dips, such as the Sector~29 data for TIC~224283342, or Sector~5 of
TIC~294328885, the dip depths typically increase by of order a few
percent over ten to twenty days.  This growth rate yields a mass flux
one order of magnitude larger than the earlier estimate.

@@

%\subsection{Are half-cycles important?}
%
% NOTE to arxis readers: the answer was: "maybe in a few cases, but
% this manuscript was already too long!".
%
%The interval of half a cycle period could be significant in the
%context of CPVs for two reasons.  The first is that for material on a
%circular orbit viewed edge-on, a half-cycle corresponds to the
%interval between transit and secondary eclipse.  The second is that
%the half-cycle also corresponds to the interval over which half of the
%star's surface is visible.  Of the CPVs in Figures~\ref{fig:cqvs}
%and~\ref{fig:evoln}, a fraction that seems greater than random might
%exhibit a preference for showing dips or peaks that correspond to the
%half-cycle interval.
%
%One set of CPVs shows ``CPV behavior'' (some form of dip complex), but
%which only lasts for half of any given cycle.  TIC~206544316 (Sector
%2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
%(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
%TIC~312410638 (Sector 38) seem to show the same tendency.
%
%An independent set of CPVs exhibits small dips roughly half a cycle
%after large dips; it is tempting to label the small dips secondary
%eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
%the sharpest, deepest minimum), TIC~89463560 (Sector 36),
%TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
%particular case of TIC~224283342, this observation, coupled with Gaia
%DR3 radial velocities suggesting a radial velocity scatter exceeding
%20\,\kms, suggests that the system could be a low-mass eclipsing
%binary transiting a giant polar spot, analogous to TOI-3884
%\citep{2022A&A...667L..11A}.
%
%In general however, it is challenging to interpret the significance of
%the potential ``half-period regularities'';  the CPVs exhibit such a
%wide range of variability that for seemingly any regularity one might
%posit, it is easy to come up with counter-example objects which do not
%follow the trend.  In other words, these half-cycle CPVs could simply
%be a product of the human tendency to pattern match.

@@

		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B star connection.}
      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
      predominantly dipolar magnetic fields known to host
      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
      are analogous magnetic B stars with field topologies potentially dominated by
      high order multipoles.  The bottom row compares the latter
      systems against the ``best-matching'' CPV light curves, selected
      by eye from Figure~\ref{fig:cqvs}.  CPVs have light curves that
      are visually similar to the topologically complex magnetic B
      stars.  Stellar masses rounded to one significant figure are
      given in the lower right of each panel; the star, TESS sector,
      and period are listed in each subtitle.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}

@@

      and depths of $\approx$1-3\% (Figures~\ref{fig:cqvs}

@@

      dur}$ (Figure~\ref{fig:cqvs}).  The dips are often superposed
      on a quasi-sinusoidal signal that presumably originates from
      starspots and faculae on the stellar surface.  The
      only viable explanation currently known for sharp dips being superposed on

>>>>

\author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
\affiliation{\princeton}

@@

In both models, the corotation radius is the location at which matter
concentrates.  The empirical basis for this is that the sharp CPV
features are superposed over smooth, quasi-sinusoidal starspot
profiles.  The theoretical importance of the corotation radius has
been noted in previous studies of magnetic rotators
\citep[e.g.][]{1973ApJ...184..271L,1985Ap&SS.116..285N,1991ApJ...370L..39K,2005ApJ...634.1214L}.
In regions where the magnetic field dominates the flow (i.e.~$B^2/8\pi
> \rho v^2 /2$), matter is dragged along with the field lines.  Within
such regions, charged gas or dust can become trapped at corotation
because of the four relevant forces -- gravity, Lorentz, inertial
Coriolis, and inertial centrifugal -- the Lorentz and Coriolis only
act perpendicular to field lines, while gravity and the centrifugal
force are in balance at $R_{\rm c}$ \citep[e.g.][their
Section~2]{2005MNRAS.357..251T}.  Another way to phrase this statement
is that, in the corotating frame, the effective potential experienced
by charged particles tends to have local minima at $R_{\rm c}$; given
a flow from either the star or from a tenuous accretion disk, this
local potential minimum enables material to build up
\citep{2005MNRAS.357..251T}.

@@

We searched for CPVs by analyzing the short-cadence data acquired by
TESS between 2018 July 25 and 2022 September 1 (Sectors 1-55).
Specifically, we used the 2-minute cadence light curves produced by
the Science Processing and Operations Center at the NASA Ames Research
Center \citep{2016SPIE.9913E..3EJ}.  While the TESS data products from
these sectors also included full frame images with cadences of 10 and
30 minutes for a larger number of sources, we restricted our attention
to the 2-minute data for the sake of uniformity and simplicity in data
handling.  In exchange, we sacrificed both completeness and
homogeneity of the selection function.  While TESS cumulatively
observed $\approx$90\% of the sky for at least one lunar month between
2018 July and 2022 September, the 2-minute cadence data were collected
for only a subset of observable stars that were preferentially nearby
and bright \citep[see][]{2021PASP..133i5002F}.  The total 2-minute
data volume from Sectors 1-55 included 1{,}087{,}475 short-cadence
light curves, which were available for 428{,}121 unique stars.

% latter stats from MERGED_spoc2min_sector1_to_sector58.csv

@@

Peaks of significance were found for $\approx$10\% of the searched
stars.  For all such cases, we generated an interim ``summary sheet''
with information about the star, its full and folded light curves,
Fourier transform, potential contaminating stars, and information
about these contaminating stars.  We then reviewed each summary sheet,
and tentatively classified each light curve based on visual inspection
of its morphology (with common categories including eclipsing binary,
CPV, RS CVn, and cataclysmic variable).

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f3.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf Validation plots used to classify CPVs}.  The complete figure
      set  is available in the online journal and contains one image per sector for each of the \nallcands\
      objects in Table~\ref{tab:thetable}.
      {\bf For internal collaboration review:
      \url{https://www.dropbox.com/sh/khtwk5a6z0zgrif/AABRG21Ire7VS4BUnaD1hOR8a?dl=0}}.
      Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
      The adopted period is given in the lower-right corner.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
      {\it c)}: DSS finder chart, with 21$''$ and 42$''$ radius
      circles for scale.  One TESS pixel has a full side length of
      21$''$.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram. The gray
      background denotes stars within 100\,pc from
      \citet{2021A&A...649A...6G}.
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN\,$\Sigma$ v1.2 association probabilities,
      calculated using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f4.pdf}
    \vspace{-0.3cm}
		\caption{
      {\bf CPVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CPVs in the high quality sample.  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Objects are ordered such
      that sources with the most TESS data available are on top (see
      Section~\ref{sec:catalog}).  Zero phase is chosen to correspond
      to minimum light.  Each panel is labeled by the TIC identifier,
      the TESS sector number, the period in hours, and the three-bit
      binarity flag from Table~\ref{tab:thetable}, which denotes Gaia
      DR3 \texttt{radial\_velocity\_error} outliers (bit 1), Gaia DR3
      \texttt{ruwe} outliers (bit 2), and stars with secondary TESS
      periods (bit 3). 
		}
		\label{fig:cpvs}
	\end{center}
\end{figure*}

@@

Figure~\ref{fig:cpvs} is a mosaic of phased light curves for the
\ngoods\ CPVs.  The objects are sorted first in order of the number of
TESS 2-minute cadence sectors in which they clearly demonstrated the
CPV phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 (12 sectors);
TIC~402980664 (7 sectors); TIC~89463560 (5 sectors); TIC~363963079 (5
sectors); and TIC~294328887 (4 sectors).  The brightest five CPVs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.

@@

@@

TIC~142173958 and TIC~425937691 both show evidence for two separate
CPV signals in their TESS light curves.  For TIC~142173958, the
signals have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691,
the two periods are 4.82\,hr and 3.22\,hr, near the 3:2 period
commensurability.  Given that both sources have two photometric
signals and elevated RUWEs, each source is probably an unresolved
binary consisting of two CPVs.  To our knowledge, these are the third
and fourth such systems known: EPIC~204060981 has two CPVs with
periods of 9.59\,hr and 9.12\,hr \citep{2018AJ....155...63S}, and
TIC~242407571 has two CPVs with periods of 11.33\,hr and 13.63\,hr,
near the 6:5 period commensurability \citep{2021AJ....161...60S}.

%\footnote{TIC~242407571, although within
%our nominal distance and brightness limits, was not observed by TESS
%in the 2-minute cadence mode between 2018~July and 2022~September, and
%is therefore not in our sample.}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.6cm}
		\caption{
			{\bf Evolution of CPV light curves over two years.}
			Out of the \ngoods\ CPVs in Figure~\ref{fig:cpvs}, 32 had
			2-minute cadence TESS data available for a baseline of at
			least two years; the 27 brightest are shown here due to space
			constraints.  Each panel shows one sector of TESS data, and is
			phased to its deepest minimum in flux.  Each panel's title shows
			the TIC identifier and period in hours.  Text insets
			show the TESS sector numbers, which generally span two years, or
			at least 1{,}000 cycles.  The vertical scale is fixed across
			sectors to clarify shape changes.  Gray circles are raw 2-minute
			data; colored circles bin to 300 points per cycle. 
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

Based on the fraction of sources that ``turned off'', the
observed shape evolution implies that CPVs have an on-off duty cycle
of $\approx$75\%.  Correcting for the duty cycle might be important in
population-level estimates of the intrinsic frequency of the CPV
phenomenon \citep[e.g.][]{2022AJ....163..144G}.

@@

@@

Curiosities include the four binary systems that are now known to each
host two separate CPVs.  CPVs are sufficiently rare that such systems
may have physical import.  Recent work has shown that the orbits of
binaries closer than $\lesssim$700 AU tend to be aligned with their
planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If we assume
that observing CPV variability requires high line-of-sight
inclinations, and that the inclinations in binaries are correlated,
then we would expect the detection of one CPV in a binary system to
raise the probability that the other star is a CPV.  The limitations
of the current catalog prevent further exploration of this issue, but
it might be interesting for future study.

A separate possible relation between binarity and CPVs is that the
presence of a binary companion could cause early disk dispersal,
freeing the star to contract.  The CPV phenomenon seems to require
rapid rotation; thus if binary systems tend to produce more rapidly
rotating stars, we would expect a sample of CPVs to have a larger
binary fraction than the field.  However, we see minimal evidence for
such an effect (Section~\ref{subsec:resultsbinarity}).  The
multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
\citep{2019AJ....157..216W}.  The $\approx$32\% multiplicity fraction
in our CPV sample (from RUWE$_{\rm DR3}$; see
Section~\ref{subsec:resultsbinarity}) seems approximately consistent
with this field fraction.

@@

Examining Figure~\ref{fig:cpvs}, it is clear that CPV dips can be
asymmetric but it is not obvious whether there is a preference for
sharper ingresses or sharper egresses.  In some cases (e.g.
TIC~425933644), the flux variations do not resemble isolated dips,
making the meaning of ``ingress'' and ``egress'' unclear.  In other
cases, such as Sector~36 of TIC~89463560, there is a sharp drop with
an exponential return to the baseline flux, resembling the signatures
of exocomets \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
and the outflowing exospheres of some transiting planets
\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.

@@

Both the dust clump and the gas prominence scenarios
(Figure~\ref{fig:f1} and Section~\ref{sec:intro}) invoke clumps of
material at the corotation radius; one property that distinguishes the
two ideas is the composition of the material.

@@

Assuming for the moment that the obscuring material is dust, we can
estimate the mass of a transiting clump. First, we convert the transit
depth into an effective cloud radius, $R_{\rm cloud}$.  For most CPVs
in Figure~\ref{fig:cpvs}, this yields $\approx$2-20\,$R_\oplus$.  A
minimum constraint on the number density of dust particles is obtained
by requiring the cloud to be optically thick.  For cases like LP
12-502, this is reasonable because the transit duration of the
shortest dips implies $R_{\rm cloud}\ll R_\star$.  Carrying out the
relevant calculation assuming the dust grains are 1\,$\mu$m in size,
\citet{2023MNRAS.518.4734S} reported minimum cloud masses of order
$10^{12}$\,kg (their Eq.~23), which scale linearly with both the
optical depth and dust grain radius.  This is comparable to a small
asteroid; the asteroid belt itself has a mass of order
$\approx$10$^{21}$\,kg \citep{2019Icar..319..812P}.  A similar
calculation that assumed occulting clumps of hydrogen, rather than
dust, derived gas prominence masses of at least $10^{14}$\,kg
\citep{1990MNRAS.247..415C}, about 100$\times$ larger than the lower
limit on the dust mass.

If the disappearance of a dip represents the permanent loss of the
obscuring material -- for example, if it is the result of a dust clump
being accreted or ejected -- then we can also estimate the rate at
which mass is flowing through the structures that lead to dips.  For
instance, LP~12-502 showed three ``state-switch'' events over the six
months of available TESS observations, during cycles 261, 309, and
1241 (Figure~\ref{fig:lpriver0}).  The other source for which we
performed a comparable analysis, TIC~300651846
(Appendix~\ref{app:tic3006}), showed two state-switches over 11
months.  In all such cases, at least one dip turned off.  For purposes
of estimation, we will take LP 12-502 as our prototype.  Assuming the
occulting material is dust, the corresponding $\dot{M} \equiv M\cdot
{\rm d}N/{\rm d}t$ time-averaged over six months is
$\approx$$1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered
cumulatively over the $\approx$$10^8$ years for which the CPV
phenomenon is observed, this yields a cumulative moved dust mass of
$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.  If
the occulting material is gas, the lower mass bounds would be of order
100 times larger.  For cases in which we observe the {\it growth} of
dips, such as the Sector~29 data for TIC~224283342, or Sector~5 of
TIC~294328885, the dip depths typically increase by of order a few
percent over ten to twenty days.  This growth rate yields a mass flux
one order of magnitude larger than the earlier estimate.

@@

%\subsection{Are half-cycles important?}
%
% NOTE to arxis readers: the answer was: "maybe in a few cases, but
% this manuscript was already too long!".
%
%The interval of half a cycle period could be significant in the
%context of CPVs for two reasons.  The first is that for material on a
%circular orbit viewed edge-on, a half-cycle corresponds to the
%interval between transit and secondary eclipse.  The second is that
%the half-cycle also corresponds to the interval over which half of the
%star's surface is visible.  Of the CPVs in Figures~\ref{fig:cpvs}
%and~\ref{fig:evoln}, a fraction that seems greater than random might
%exhibit a preference for showing dips or peaks that correspond to the
%half-cycle interval.
%
%One set of CPVs shows ``CPV behavior'' (some form of dip complex), but
%which only lasts for half of any given cycle.  TIC~206544316 (Sector
%2) is a canonical example; TIC~405910546 (Sector 38), TIC~167664935
%(Sector 38), TIC~146539195 (Sector 5), TIC~118449916 (Sector 44), and
%TIC~312410638 (Sector 38) seem to show the same tendency.
%
%An independent set of CPVs exhibits small dips roughly half a cycle
%after large dips; it is tempting to label the small dips secondary
%eclipses.  Such sources include TIC~402980664 (Sector 25; relative to
%the sharpest, deepest minimum), TIC~89463560 (Sector 36),
%TIC~224283342 (Sector 2), and TIC~442571495 (Sector 12).  For the
%particular case of TIC~224283342, this observation, coupled with Gaia
%DR3 radial velocities suggesting a radial velocity scatter exceeding
%20\,\kms, suggests that the system could be a low-mass eclipsing
%binary transiting a giant polar spot, analogous to TOI-3884
%\citep{2022A&A...667L..11A}.
%
%In general however, it is challenging to interpret the significance of
%the potential ``half-period regularities'';  the CPVs exhibit such a
%wide range of variability that for seemingly any regularity one might
%posit, it is easy to come up with counter-example objects which do not
%follow the trend.  In other words, these half-cycle CPVs could simply
%be a product of the human tendency to pattern match.

@@

		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B star connection.}
      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
      predominantly dipolar magnetic fields known to host
      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
      are analogous magnetic B stars with field topologies potentially
      dominated by high order multipoles.  The bottom row compares the
      latter systems against the ``best-matching'' CPV light curves,
      selected by eye from Figure~\ref{fig:cpvs}.  CPVs have light
      curves that are visually similar to the topologically complex
      magnetic B stars.  Stellar masses rounded to one significant
      figure are given in the lower right of each panel; the star,
      TESS sector, and period are listed in each subtitle.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}

@@

      and depths of $\approx$1-3\% (Figures~\ref{fig:cpvs}

@@

      dur}$ (Figure~\ref{fig:cpvs}).  The dips are often superposed on
      a quasi-sinusoidal signal that presumably originates from
      starspots and faculae on the stellar surface.  The only viable
      explanation currently known for sharp dips being superposed on
      the starspot signals is that concentrations (``clumps'') of
